|

### 2021-03-15 02-Chp-Background.Rmd
Send draft of Chapter 2 to Ciara
End of day

@@

``` {r}
library(gt)
library(dplyr)

gt(data = mtcars) %>%
  tab_style(
    style = cell_text(weight = "bold"),
    locations = list(cells_body(
      columns = vars(mpg)),
      cells_column_labels(columns = vars(mpg))))

```

@@

*Cognitive impairment not dementia* (CIND) is another term used to described those with cognitivie impairment but who fall below the diagnostic criteria for dementia.

@@

There exist only two large scale randomized controlled trials - in fact these studies are the only two trials included in a 2016 review of statins for the prevention of dementia produced by the Cochrane [@mcguinness2016b]. Both showed no effect of

@@

@@

>>>>

This thesis is

Lay summaries appear at the beginning of each chapter, reviewed by the Patient and Public Involvement P

@@

@@

*Cognitive impairment not dementia* (CIND) is another term used to described those with cognitive impairment but who fall below the diagnostic criteria for dementia.

@@

There exist only two large scale randomized controlled trials of the effect of statins on dementia risk - in fact these studies are the only two trials included in a 2016 review of statins for the prevention of dementia produced by the Cochrane [@mcguinness2016b]. Both showed no effect of

However, while being widely cited,

@@

The economic impact of dementia is enormous, but in terms of the direct care required

Patients with dementia stay in hospital for longer,[@mollers2019]

Patients are more prone to falls and other con

@@

he main theoretical framework used in this thesis is evidence synthesis - the identification, critical assessment, and integration of all available evidence on a research question in order to either: a) provide a more definitive answer to that question; or b) highlight gaps in the existing evidence base.

While this thesis does include a research tool (Chapter 2 - systematic searching of preprint) and a primary evidence generation element (Chapter 5 - observational analysis of CPRD data), this was performed with the intention of providing a further source of evidence for the evidence synthesis/triangulation aspect of the thesis.

### 2021-03-15 04-Chp-Systematic-Review.Rmd
End of day

>>>>

### Comments on the process

Systematic reviews should not be performed as part of a thesis, without suitable support and resourcing guaranteed. Assumption that everyone does a systematic review (without risk of bias assessments, inclusion of all literature, searching for other reviews) is foolish.

Great learning experience in terms of managing a team, but due to a rotating schedule of people, much harder to do that expected.

A final point on the progress of the review is that, due to the need for dual screening and data extraction, a number of external researchers became involved in this review. I found the people-management aspect particularly challenging and could definitely have improved the process through better communication of deadlines, but it has provided good experience of leading a review team.

### Original contribution to research

I believe there are three aspects where this review is distinct from those reviews already available in the published literature (as identified by [CITE]):

* _Comprehensiveness:_ While several reviews of this research topic exist,[@chu2018b; @yang2020; @muangpaisan2010; @poly2020b] the overlap between the list of studies included in each is not 100%. As part of this review, I have not only performed a original search of primary literature databases, but have also screened the reference lists of comparable reviews to ensure no study has been omitted.
* _Structured risk of bias assessment:_ The majority of the highly cited reviews on this topic either do not formally consider the risk of bias in the observational studies they include or do not use an appropriate domain-based assessment tool (e.g. ROBINS-I/E). This is important area in which this thesis can add value, as based on the risk-of-bias assessments I have performed to date, several primary studies are at high risk of bias and this should be reflected in the findings of any  review on this topic.
* _Inclusion of preprints:_ Unlike other available reviews and enabled by the tool described in Chapter 3, this review systematically searched  preprinted health-related manuscripts as a source of grey literature. As part of this chapter, I plan to examine the extent of the additional information provided to the review by the inclusion of preprints.

### 2021-03-15 05-Chp-CPRD-Analysis.Rmd
End of day

## Covariates

@@

Potential biases included time varying confounding, selection bias due to censoring on death and 
We performed a Cox

@@

### Replicating the analysis

@@

As part of our exploration of the, we chose to explore whether our results were comparable with

As discussed in

@@

## Main findings

@@

## Comparison to other literature

@@

## Strengths and Limitations

@@

## Conclusions

>>>>

### Covariates

@@

Potential biases included time varying confounding, selection bias due to censoring on death and 
We use a Cox proportional hazards model with a time-varying treatment indicator.

@@

### Replicating other analytical strategies

@@

As part of our exploration of the unexpected results,

]

@@

### Main findings

@@

### Comparison to other literature

@@

### Original contribution to research

There are two primary ways in which this research adds to the topic:

* _Size of the CPRD and length of follow-up:_ Having reviewed the other studies identified by the systematic review in Chapter 4, this analysis of 1.7 million participants is one of the largest studies of this research question.
* _Addressing the limitations of other observational analyses:_ Analyzing this data has provided the opportunity to use a separate analytical technique to many of the studies identified in the systematic review, As an example, the Hippsley-Cox BMJ paper examining the effect of statins, which makes use of the THIN EHR database, likely suffers from immortal time bias as exposed and unexposed participants are not followed up from a common time point.[@hippisley-cox2010] As touched on in the section above, this provides an additional evidence point with a different source and direction of bias, which is useful for the triangulation aspect of the thesis.

### Strengths and Limitations

@@

### Conclusions

### 2021-03-15 97-Discussion.Rmd
End of day: -3533
End of day

@@

>>>>

## Additional topics for the discussion

There are several addition topics I would like to cover:

* The difference between the peer review of the software vs. the peer review of papers. A conversation until everything is fixed/clear reporting guidelines/checklists, with acceptance dependent on them being implemented /built-in version control, and cross linking discussion points to changes through the linking of commits and comments.  Essentially, a more transparent and open

* The management of

Doing systematic reviews as a

@@

Need for large simple trials for common disease where small treatment effect can have large effect - [@yusuf1984]
